% !TEX TS-program = XeLaTeX
% !TEX encoding = UTF-8 Unicode

\song\wuhao
\linespread{1.25}
\chapter*{\hfill 参~考~文~献 \hfill}
\addcontentsline{toc}{chapter}{参~考~文~献}
\label{reference}

\begin{thebibliography}{99}
\bibitem{halperin2011csi}
Halperin D, Hu W, Sheth A, et al. Tool release: gathering 802.11n traces with channel state information[J]. ACM SIGCOMM Computer Communication Review, 2011, 41(1): 53.

\bibitem{indotrack2017}
Li X, Zhang D, Lv Q, et al. IndoTrack: Device-free indoor human tracking with commodity Wi-Fi[J]. Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies, 2017, 1(3): 1-22.

\bibitem{signfi2018}
Ma Y, Zhou G, Wang S, et al. SignFi: Sign language recognition using WiFi[J]. Proceedings of the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies, 2018, 2(1): 1-21.

\bibitem{svm1995}
Cortes C, Vapnik V. Support-vector networks[J]. Machine Learning, 1995, 20(3): 273-297.

\bibitem{randomforest2001}
Breiman L. Random forests[J]. Machine Learning, 2001, 45(1): 5-32.

\bibitem{extratrees2006}
Geurts P, Ernst D, Wehenkel L. Extremely randomized trees[J]. Machine Learning, 2006, 63(1): 3-42.

\bibitem{tcn2018}
Bai S, Kolter J Z, Koltun V. An empirical evaluation of generic convolutional and recurrent networks for sequence modeling[J]. arXiv preprint arXiv:1803.01271, 2018.

\bibitem{csikit2021}
Forbes G. CSIKit: Python CSI processing and visualisation toolkit[EB/OL]. 2021. https://github.com/Gi-z/CSIKit.

\bibitem{eeyes2014}
Wang Y, Liu J, Chen Y, et al. E-eyes: Device-free location-oriented activity identification using fine-grained WiFi signatures[C]//Proceedings of the 20th Annual International Conference on Mobile Computing and Networking. 2014: 617-628.

\bibitem{carm2015}
Wang W, Liu A X, Shahzad M, et al. Understanding and modeling of WiFi signal based human activity recognition[C]//Proceedings of the 21st Annual International Conference on Mobile Computing and Networking. 2015: 65-76.

\bibitem{survey2019}
Ma Y, Zhou G, Wang S. WiFi sensing with channel state information: A survey[J]. ACM Computing Surveys, 2019, 52(3): 1-36.

\bibitem{crosssense2018}
Jiang W, Miao C, Ma F, et al. Towards environment independent device free human activity recognition[C]//Proceedings of the 24th Annual International Conference on Mobile Computing and Networking. 2018: 289-304.

\bibitem{widar2019}
Zheng Y, Zhang Y, Qian K, et al. Zero-effort cross-domain gesture recognition with Wi-Fi[C]//Proceedings of the 17th Annual International Conference on Mobile Systems, Applications, and Services. 2019: 313-325.
\end{thebibliography}
